\Title

### 2023-06-01 Grimaldi-etal-BiolCybernetics.tex
Another pass

    	Representation of the weights for $8$ directions for one speed (among the $8 \times 3$ different kernels of the model) as learned on the dataset of naturalistic scenes. Directions are shown as red arrows on the left. The spatio-temporal kernels are represented as slices of spatial weights at different delays. Delays vary along the horizontal axis from the far right (delay of one step) to the left (delay of $12$ steps). Each image corresponds to the weights at a given delay, with excitatory and inhibitory weights in warm and cold colors, respectively. Due to the symmetry between the ON and OFF event streams, we report that the kernels for the OFF polarities are very similar and are not shown here.	Different kernels are selective to the different motion directions, and we observe for all kernels an orientation preference perpendicular to the orientation. 
%      % These weights are associated to a specific delay on the \textit{delays} axis and to a presynaptic address defined on the two other axes. %	For the sake of clarity, the values in range $[-0.05, 0.05]$ are not shown.    One sees positive (excitatory) coefficients for the specific direction of motion but also negative (inhibitory) coefficients for other directions.

@@

After training our model, we first analyze the weights learned for the different neurons (\seeFig{kernels}). We first notice that these cells are very localized along each trajectory, yet show an orientation selectivity, similar to that detected in MT neurons~\citep{deangelis_functional_1999}. Focusing on the positive weights, a strong selectivity is observed along specific axes of motion for each of the different kernels. These directions can be easily associated to the direction of motion controlled in the natural images and show a typical anisotropic profile~\citep{kaplan_anisotropic_2013}. For instance, the first kernel shows a strong selectivity to a downward motion direction.
We also observed a high dependence between the weights reaching the ON polarities and that reaching the OFF polarities. In particular, whenever a weight for a given position and delay is positive for one polarity, it will be negative in the other. This property comes from the way the events are generated and that the luminance can not at the same time increase and decrease.  Interestingly, the relative organization of the receptive fields in quadrature of phase follows a push-pull organization predicted by~\citet{kremkow_push-pull_2016} to explain neurophysiological results obtained after showing similar natural scenes with synthetic eye movements~\citep{baudot_animation_2013}. %ith the negative weights, one can observe an anti-selectivity for directions that do not correspond to the motion to which the kernel is selective to. 
%This qualitative look at the 3D kernels allows the reader to infer for the $8$ different motion directions used to generate our synthetic event streams.

@@

Such recurrent activity would be essential for the implementation of predictive or anticipatory processes. This is essential in a neural system because it contains several different delays that require temporal alignment~\citep{hogendoorn_predictive_2019}. This has been modeled before to explain, for example, the flash-lag illusion~\citep{khoei_flash-lag_2017}. %\note{Say that this could be implemented by properly setting the timing of the label} 
As mentioned previously, this could be implemented using generalized coordinates (i.e., variables such as position complemented by motion, acceleration, jerk,~\ldots), and ``neurobiologically, using delay operators just means changing synaptic connection strengths to take different mixtures of generalized sensations and their prediction errors''~\citep{perrinet_active_2014}. Our proposed model using heterogeneous delays provides an alternative and elegant implementation solution to this problem.
%
\subsection{Perspectives}
%%%-----------------------------------------------------------------
% \note{la tache ne met pas en avant les capacites des motifs hetero synaptiques =trop simple et peut se faire en HOTS}
In defining our task, we emphasized that the generation of events depends on the spatial gradient in each image. This gradient has both horizontal and vertical dimensions, and its maxima are generally orientation dependent. Taken together, these oriented edges form the contours of visual objects in the scene~\citep{koenderink_representation_1987}. Thus, there is an interdependence between the information about motion and the information about orientation within the event stream. It would be crucial to investigate this dependency further. This could be initiated by training the model on a dataset with labels that provide local orientation. %\note{we can say that we tried it and that it works well}. 
Exploring this dependence will allow us to dissociate these two forms of visual information and enable us to integrate them. In particular, it will allow us to consider that the definition of motion is more accurate perpendicular to an oriented contour (aka the aperture problem). Thus, it will allow us to implement recurrent prediction rules, such as those identified to dissociate this problem~\citep{perrinet_motion-based_2012}.

>>>>

    	Representation of the weights for $XXX8$ directions for a single speed (among the $XXX8 \times XXX3$ different kernels of the model) as learned on the dataset of naturalistic scenes. The directions are shown as red arrows in the left insets. The spatiotemporal kernels are shown as slices of spatial weights at different delays. Delays vary along the horizontal axis from the far right (delay of one step) to the left (delay of $12$ steps). Each image corresponds to the weights at a given delay, with excitatory and inhibitory weights in warm and cold colors, respectively. Due to the symmetry between the ON and OFF event streams, we report that the kernels for the OFF polarities are very similar and are not shown here.	Different kernels are selective for the different motion directions, and we observe a slight orientation preference perpendicular to direction for all kernels.

@@

After training our model, we first analyze the weights learned for the different neurons (\seeFig{kernels}). We first notice that these cells are very localized along each trajectory, but show an orientation selectivity similar to that found for MT neurons~\citep{deangelis_functional_1999}. Focusing on the positive weights, a strong selectivity along specific motion axes is observed for each of the different kernels. These directions can be easily associated with the direction of motion controlled in the natural images and show a typical anisotropic profile~\citep{kaplan_anisotropic_2013}. For example, the first kernel shows a strong selectivity for a downward direction of motion. Note that as the delays become larger, the coefficients become lower and less localized, consistent with the average diffusion of information included in the generative model and with the diffusion introduced in motion-based prediction models~\citep{perrinet_motion-based_2012,khoei_flash-lag_2017}. We also observed a strong dependence between the weights reaching the ON polarities and those reaching the OFF polarities. In particular, whenever a weight for a given position and delay is positive for one polarity, it will be negative for the other. This property is due to the way the events are generated and the fact that the luminance cannot increase and decrease at the same time.  Interestingly, the relative organization of the receptive fields in quadrature of phase follows a push-pull organization predicted by~\citet{kremkow_push-pull_2016} to explain neurophysiological results obtained after showing similar natural scenes with synthetic eye movements~\citep{baudot_animation_2013}.

@@

Such recurrent activity would be essential for the implementation of predictive or anticipatory processes. This is essential in a neural system because it contains several different delays that require temporal alignment~\citep{hogendoorn_predictive_2019}. This has been modeled before to explain, for example, the flash-lag illusion~\citep{khoei_flash-lag_2017}. %\note{Say that this could be implemented by properly setting the timing of the label} 
As mentioned previously, this could be implemented using generalized coordinates (i.e., variables such as position complemented by motion, acceleration, jerk,~\ldots), and ``neurobiologically, using delay operators just means changing synaptic connection strengths to take different mixtures of generalized sensations and their prediction errors''~\citep{perrinet_active_2014}. Our proposed model using heterogeneous delays provides an alternative and elegant implementation solution to this problem.
\subsection{Perspectives}
%%%-----------------------------------------------------------------
% \note{la tache ne met pas en avant les capacites des motifs hetero synaptiques =trop simple et peut se faire en HOTS}
In defining our task, we emphasized that the generation of events depends on the spatial gradient in each image. This gradient has both horizontal and vertical dimensions, and its maxima are generally orientation dependent. Taken together, these oriented edges form the contours of visual objects in the scene~\citep{koenderink_representation_1987}. Thus, there is an interdependence between the information about motion and the information about orientation within the event stream. It would be crucial to investigate this dependency further. This could be initiated by training the model on a dataset with labels that provide local orientation. %\note{we can say that we tried it and that it works well}. 
Exploring this dependence will allow us to dissociate these two forms of visual information and enable us to integrate them. In particular, it will allow us to consider that the definition of motion is more accurate perpendicular to an oriented contour (aka the aperture problem). Thus, it will allow us to implement recurrent prediction rules, such as those identified to dissociate this problem~\citep{perrinet_motion-based_2012}.
